manuscript_figures

### 2024-08-01 scripts/manuscript_figures.Rmd
updated tables

@@

@@

# Combine the plots with patchwork
prod_combined_plot <- (production_plot | kelp.treatment) +
  plot_annotation(tag_levels = 'A') + 
  theme(plot.tag = element_text(size = 18, face = "bold"));prod_combined_plot

@@

>>>>

# Perform ANOVA on the mixed model
anova_results <- Anova(lmm_model, type = 3)
print(anova_results)

# Extract coefficients and their standard errors
model_summary <- broom.mixed::tidy(lmm_model)

@@

# Display the coefficients table
print(df)

@@

# Combine the plots with patchwork
prod_combined_plot <- (production_plot | kelp.treatment) +
  plot_annotation(tag_levels = 'A') + 
   theme(plot.tag = element_text(face = "bold", size = 18));prod_combined_plot

@@

# Make publishable table for fish production and life history information
```{r}
# read in data
life.hist <- read.csv("data/fish.life.history.data.csv")

# Create a gt table
fish_table <- gt(life.hist) %>%
  tab_header(
    title = "Fish Species Life History Traits"
  ) %>%
  fmt_number(
    columns = vars(ALPHA, BETA, Lmat, Wmat, P.B.ratio, K.growth.coefficient),
    decimals = 2
  ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_title(groups = "title")
  ) %>%
  tab_style(
    style = list(
      cell_text(weight = "bold")
    ),
    locations = cells_column_labels(everything())
  )

# Save as HTML
gtsave(fish_table, file = "output/figures/life_history_table.html")

# Save as PDF (requires the webshot2 package)
# webshot::install_phantomjs() # Run this once if you haven't installed PhantomJS
gtsave(fish_table, file = "output/figures/life_history_table.pdf", expand = 2)
